---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

# drakepkg

The goal of `drakepkg` is to demonstrate how a [`drake`](https://ropensci.github.io/drake/) workflow can be organized as an R package. 

This package is a work-in-progress that began with a request for guidance: [`drake` issue #471](https://github.com/ropensci/drake/issues/471)

The following table shows how each feature of a [`drake`](https://ropensci.github.io/drake/) workflow is made accessible within an R package: 

| `drake`                   | R Package                                                    |
|:------------------------- |:---------------------------------------------------------- |
| plans, commands           | functions (`R/*.R`)                                        |
| targets                   | stored in the cache (`.drake/`)                            |
| input files, output files | internal data (`inst/intdata/*`), external data (`inst/extdata/*`), images and documents (`inst/documents/*`)                           |

## Installation

You can install the released version of `drakepkg` from its Github [repository](https://github.com/tiernanmartin/drakepkg) with:

``` {r install, eval=FALSE}
devtools::install_packages("tiernanmartin/drakepkg")
```

## Usage

The package comes with two example [`drake`](https://ropensci.github.io/drake/) plans that are loosely based on the [`main`](https://github.com/ropensci/drake/tree/master/inst/examples/main) example included in the [`drake`](https://ropensci.github.io/drake/) package. 

The first plan is a simple one:

```{r}
library(drakepkg)

get_example_plan_simple()

```


Several commands used in the plan (e.g,`create_plot()`, `write_report_simple()`) are included as part of the `drakepkg` R package and so is the plan itself; the documentation for each of these functions can be accessed using R's `help()` function (for example, `help(get_example_plan_simple)`).

You can reproduce the simple plan's workflow by performing the following steps:

  1. Copy the package's directories and source code files into your working directory with the `copy_drakepkg_files()` function
  2. View the plan (`get_example_plan_simple()`) and then make it (`make(get_example_plan_simple())`)
  3. Access the plan's targets using `drake` functions like `readd()` or `loadd()`
  4. View the html documents created by the workflow in the `documents/` directory


```{r step1, eval=FALSE}
# Step 1: copy the source code files into the working directory

copy_drakepkg_files()
```


```{r step2A}
# Step 2A: view the example plan

get_example_plan_simple()
```


```{r step2B}
# Step 2B: make the example plan

make(get_example_plan_simple())
```


```{r step4}
# Step 3: examine the plan's targets

readd(fit)

readd(hist)
```






