---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

# drakepkg

The goal of `drakepkg` is to demonstrate how a [`drake`](https://ropensci.github.io/drake/) workflow can be organized as an R package. 

This package is a work-in-progress that began with a request for guidance: [`drake` issue #471](https://github.com/ropensci/drake/issues/471)

The following table shows how each feature of a [`drake`](https://ropensci.github.io/drake/) workflow is made accessible within an R package: 

| `drake`                   | Package                                                    |
|:------------------------- |:---------------------------------------------------------- |
| plans                     | data (`data/*.rda`)                                        |
| commands                  | functions (`R/*.R`)                                        |
| targets                   | _not directly accessible (stored in the cache: `.drake/`)_ |
| input files, output files | external data (`inst/extdata/*`)                           |

## Installation

You can install the released version of `drakepkg` from its Github [repository](https://github.com/tiernanmartin/drakepkg) with:

``` r
devtools::install_packages("tiernanmartin/drakepkg")
```

## Usage

The package comes with one plan (`plan_example`) which is saved as a data object.

```{r}
library(drakepkg)

plan_example
```

The plan is based on the [`main`](https://github.com/ropensci/drake/tree/master/inst/examples/main) example included in the [`drake`](https://ropensci.github.io/drake/) package. 

One of the functions used in the plan — `create_plot()` — is made specifically for this example and its documentation can be accessed using `help(create_plot)`.

You can create `drakepkg`'s workflow by performing the following steps:

  1. Copy the workflow's directories and source code files into your working directory with the `copy_pkg_files()` function
  2. Run `make(plan_example)`
  3. Access the `plan_example` targets using `drake` functions like `readd()` or `loadd()`


```{r}

# Step 1: copy the source code files into the working directory

copy_pkg_files()


# Step 2: make the example plan

make(plan_example)


# Step 3: examine the plan's targets

readd(fit)

loadd(hist)

print(hist)

```







