---
title: "1. How to use a packaged `drake` workflow"
author: "Tiernan Martin"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{1. How to use a packaged `drake` workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/vignette-",
  comment = "#>"
  )
  options(drake_make_menu = FALSE,
  drake_clean_menu = FALSE)
```
  
The goal of `drakepkg` is to demonstrate how a [`drake`](https://ropensci.github.io/drake/) workflow can be organized as an R package. Users who are not yet familiar with [`drake`](https://ropensci.github.io/drake/) should review the package's [User Manual](https://ropenscilabs.github.io/drake-manual/) before continuing with this vignette.
  
The following examples illustrate the way that [`drake`](https://ropensci.github.io/drake/) workflow's can be reproduced when they're included in an R package.
  
# Simple Plan
  
This example borrows the `main` example from the [`drake`](https://ropensci.github.io/drake/) package documentation and recreates it within an R package.
  
The plan is included in `drakepkg` as a function:
  
```{r simple-plan}
library(drakepkg) # devtools::install_packages("tiernanmartin/drakepkg")

get_example_plan_simple()
```

Here are the steps needed to reproduce this plan:

1. Create a new [RStudio Project](https://support.rstudio.com/hc/en-us/articles/200526207-Using-Projects) or navigate to an empty working directory (not _required_ but strongly recommended)
2. Copy the package's directories and source code files into your working directory: `copy_drakepkg_files()`
3. Make the plan: `make(get_example_plan_simple())`
4. Access the plan's targets using `drake` functions like `readd()` or `loadd()`
5. View the html documents produced by the workflow (see the `documents/` directory)

The first step is optional but strongly recommended; it is generally accepted as a best practice that data analysis projects should be [self-contained](https://www.tidyverse.org/articles/2017/12/workflow-vs-script/#self-contained-projects).  

The second step is an important one. Most [`drake`](https://ropensci.github.io/drake/) plans interact with the user's file system at some point, typically to read inputs or write outputs. `drakepkg`'s `inst/` directory contains the files and directories that are needed to successfully make `get_example_plan_simple()`. The `copy_drakepkg_files()` function copies the following directories from `drakepkg` into the user's working directory:

```{r simple-step2-noeval}
copy_drakepkg_files()
```

```
.
├── documents
├── extdata 
└── intdata
    ├── R
    │   └── make-iris-internal.R
    └── iris-internal.xlsx 
```
The third step is to make the plan:

```{r simple-step3-noecho, echo=FALSE}
clean(destroy = TRUE) 
```


```{r simple-step3}  
make(get_example_plan_simple())
```

The worflow's dependency graph can be displayed using `drake::vis_drake_graph()`:

```{r simple-vis, out.width = "100%"}
get_example_plan_simple() %>% 
  drake_config() %>% 
  vis_drake_graph()
```

The final output of the plan above is the `report` target but any of the targets
can be accessed using [`drake`](https://ropensci.github.io/drake/) functions like
`loadd()` or `readd()`.

```{r simple-hist-noeval, out.width="80%"} 
# retrieve a target from the drake cache and inspect it
loadd(fit)
summary(fit) 

# inspect a target without storing it in the local environment
readd(hist) 
```


# Plan With External Data

The second example builds on the first by introducing external data. The [`drake`](https://ropensci.github.io/drake/) cache automatically stores a copy of each target in a plan, but when the plan accessess data from 
an external source it's a good idea to store a local copy of that data in addition to the cached copy.

The following plan downloads the `iris` dataset from a github repository and stores it in the `extdata` directory in the user's working directory, like so:

```
.
├── documents
├── extdata
|   └── iris-external.xlsx <-- file downloaded in the plan is stored here
└── intdata
    ├── R
    │   └── make-iris-internal.R
    └── iris-internal.xlsx 
```
Here is the plan:

```{r external-clean, echo=FALSE}
clean(destroy = TRUE) 
```

```{r external-make} 
make(get_example_plan_external())
```

```{r external-vis, out.width = "100%"}
get_example_plan_external() %>% 
  drake_config() %>% 
  vis_drake_graph()
```

The visualization below shows that the new "`iris`" data is actually just random 
numbers:

```{r external-hist, out.width = "80%"} 
readd(hist)
```


# Plan With Open Science Framework Compendium
_(work in progress)_
